### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

\vspace{1.0ex}
We next develop an incremental approach to handling pattern and data updates in a unified framework, based on {\em pattern fragmentation} and {\em affected balls}
to localize the impacts of pattern and data updates and to reduce the cost of maintaining auxiliary structures and computations.

@@

\stitle{Pattern fragmentation}. We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

We also refer to $P_{fi}$ ($i\in[1,h]$) as a {\em fragment} of $P$, and $C$ as a {\em cut} of $P$, respectively.

Observe that by pattern fragmentation, a pattern update on $P$ is either on a fragment $P_{fi}$ or on the cut $C$ of $P$, and, in this way, the impact of pattern updates is localized. %to some extent.

\vspace{0.5ex}
Graph simulation has a nice property as follows.

\vspace{-0.5ex}
\begin{theorem}
\label{thm-compose}
Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
For any ball $\ball{}$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}$ for $P_{fi}$ via graph simulation,
and $M$ be the maximum match relation in $\ball{}$ for $P$ via graph simulation, respectively,
then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
\end{theorem}

We also say that $M_i$ is a {\em partial match relations} in ball $\ball{}$ for $P$ via graph simulation.
%By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
%and then combining them together.
By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually intermediate results for computing $M$.
%such that the method above does not incur additional computation cost.
After we have the maximum match relation $M$ for $P$ in $\ball{}$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.

That is, based on pattern fragmentation, we store and maintain $\tilde{M}(P,G)$ \wrt ${\cal P}_{h}$ for the incremental process,
\ie the maximum match relations for all pattern fragments of $P$ in all balls of $G$, via graph simulation.
Moreover, its space cost is light-weight, as shown in the experiments section.
%\revise{
%Moreover, by Theorem~\ref{thm-tsim-radius}, the match results in balls $\ball{[v, t]}$ ($1 \leq t < r$) can be easily derived from the %matches in ball $\ball{[v, r]}$.
%Thus, we only store the maximum match relations for all pattern fragments of $P$ in the balls with radius $r$ of $G$.}
%which will be shown to be much more informative than storing $M(P,G)$ and $L_{k}(P,G)$.
%Its space cost is light-weight, and takes 25MB only, together with all indexes for \citationd that needs 36MB to store itself.

@@

We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
%If we have cached the maximum match relations of all pattern fragments,
By storing $\tilde{M}(P,G)$, we can get $\bigcup_{i=1}^{h}M_{i}$ for a ball $\ball{}$.
Then we can do an update computation on $M_i$ while leaving other parts unchanged. That is, to compute $P_{fi}\oplus\Delta P(\ball{})$ instead of $P\oplus\Delta P(\ball{})$, and to combine $P_{fi}\oplus\Delta P(\ball{})$ with the other parts to derive $P\oplus\Delta P(\ball{})$.
Even better, the updates $\Delta P$ on $C$ of $P$ only involve with the combination process, avoiding the computation for any pattern fragments.

\vspace{0.8ex}
\revise{During the incremental process, we typically want} (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
\revise{Intuitively, the bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
	while minimizing the cut size between pattern fragments.}

@@

\vspace{1.0ex}
So far, we have restricted the impact of pattern updates from the entire $P$ to a fraction of $P$.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid computing and updating match relations for all balls.

\stitle{Affected balls (\affballsx)}.
We say a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
if \algorithm{A} accesses the ball again.
We use $||\affballsx||$ and $|\affballsx|$ to denote the cardinality and total size of \affballsx, respectively.

>>>>

Nevertheless, we develop an incremental approach to handling pattern and data updates in a unified framework, by utilizing {\em pattern fragmentation} and {\em affected balls} to localize the impacts of pattern and data updates, and to reduce the cost of maintaining auxiliary structures and computations.

@@

\stitle{(i) Localization with pattern fragmentation}. We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

We also say $P_{fi}$ ($i\in[1,h]$) as a {\em fragment} of $P$, and $C$ as a {\em cut} of $P$, respectively.

Observe that by pattern fragmentation, a pattern update on $P$ is either on a fragment $P_{fi}$ or on the cut $C$ of $P$, and, in this way, the impact of pattern updates is localized. Moreover, graph simulation holds a nice property on pattern fragmentation, as shown below.

\vspace{-0.5ex}
\begin{theorem}
\label{thm-compose}
Let $\{P_{f1},\ldots,P_{fh}\}$ be an $h$-fragmentation of pattern $P$.
For any ball $\ball{}_i$ in $G$, let $M_i$ ($i\in[1,h]$) be the maximum match relation in $\ball{}_i$ for $P_{fi}$ via graph simulation,
and $M$ be the maximum match relation in $\ball{}_i$ for $P$ via graph simulation, respectively,
then $M\subseteq\bigcup_{i=1}^{h}M_{i}$.
\end{theorem}

We also say that $M_i$ is a {\em partial match relation} in ball $\ball{}_i$ for $P$ via graph simulation.
%By Theorem~\ref{thm-compose}, instead of computing $M$ in $\ball{}$ \wrt\ $P$ directly, we can compute $M$ by first computing each $M_i$ in $\ball{}$ \wrt\ $P_{fi}$,
%and then combining them together.
By the nature of graph simulation~\cite{infsimu95}, $\bigcup_{i=1}^{h}M_{i}$ is actually an intermediate result of $M$.
%such that the method above does not incur additional computation cost.
Once we have the maximum match relation $M$ for $P$ in $\ball{}_i$, via graph simulation, we can further produce the result for $P$ in  $\ball{}$ via team simulation, by a capacity check.

That is, based on pattern fragmentation, we maintain 
an auxiliary structure for storing fragment-ball matches for incremental computations,
\ie $\tilde{M}(P,G)$ \wrt ${\cal P}_{h}$ that is the maximum match relations for all pattern fragments of $P$ in all balls of $G$, via graph simulation.
Moreover, its space cost is light-weight, as will be shown in the experimental study.
%\revise{
%Moreover, by Theorem~\ref{thm-tsim-radius}, the match results in balls $\ball{[v, t]}$ ($1 \leq t < r$) can be easily derived from the %matches in ball $\ball{[v, r]}$.
%Thus, we only store the maximum match relations for all pattern fragments of $P$ in the balls with radius $r$ of $G$.}
%which will be shown to be much more informative than storing $M(P,G)$ and $L_{k}(P,G)$.
%Its space cost is light-weight, and takes 25MB only, together with all indexes for \citationd that needs 36MB to store itself.

@@

%We already know that pattern updates $\Delta P$ on $P$ can be treated as the updates $\Delta P$ on $P_{fi}$ or $C$ of $P$.
%If we have cached the maximum match relations of all pattern fragments,
By storing $\tilde{M}(P,G)$, we have $\bigcup_{i=1}^{h}M_{i}$ for each ball $\ball{}$,
and we can simply update $M_i$ while leaving other parts untouched. That is, we indeed compute for $P_{fi}\oplus\Delta P(\ball{})$, instead of $P\oplus\Delta P(\ball{})$, and combine all $P_{fi}\oplus\Delta P(\ball{})$ derive $P\oplus\Delta P(\ball{})$.
Even better, the updates $\Delta P$ on $C$ of $P$ only involve with a simple combination process, avoiding the computation for any pattern fragments.

For a better incremental process, we typically want (1) to avoid skewed updates by balancing the sizes of all fragments, and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define and investigate the {\em pattern fragmentation} problem.

Given pattern $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
Intuitively, the bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size while minimizing the cut size.

@@

\stitle{(ii) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.

We say a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
if \algorithm{A} accesses the ball again.
We use $||\affballsx||$ and $|\affballsx|$ to denote the cardinality and total size of \affballsx, respectively.
